Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-04 Paper/main.tex
Update paper
Edit objectives

\section{Nomenclature}
\fxnote{Update symbols}
{\renewcommand\arraystretch{1.0}
  \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
ABL       & Atmospheric Boundary Layer \\
$\alpha$  & Wind shear exponent  \\
$f$       & Frequency \\
$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
$f_{Ny}$   & Nyquist frequency \\
$L$       & Turbulent integral length scale \\
$L_{Ob}$   & Obukhov length scale \\
LES       & Large Eddy Simulation \\
$u_\tau$   & Friction velocity    \\
$\rho$    & Density \\
$\rho_\circ$ & Reference density  \\
$R_{ij}$   & Two point correlation tensor \\
SBL       & Stable Boundary Layer \\
$\theta$  & Potential temperature \\
$TI$      & Turbulence intensity \\
$TKE$     & Turbulent kinetic energy \\
$\overline{U}_{horiz}$ & Time averaged horizontal velocity
\end{longtable*}}

\section{Introduction}
%\fxnote{Update this introduction.}

@@

\subsection{Objectives}
\fxnote{fix order of objectives}
In the current study on stable marine boundary layers, we aim to build
on the previous work in the literature and complete several
objectives.  First, a series of stable boundary layer conditions will
be computed using the ExaWind solvers which match the measurements of
Archer et al. \cite{archer2016predominance}.  The behavior of the
stable boundary layers, including mean flow quantities and turbulent
statistics, are examined and compared to the neutral and unstable
cases computed in \cite{cheung2020large}.  Secondly, we examine the
domain and mesh requirements necessary to capture the turbulent scales
for the stable offshore boundary layers.  Finally, two LES solvers
within the ExaWind project are compared in this study: the
unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
used to calculate the same SBL, and the relative differences between
the codes are reported.

>>>>

\section{Nomenclature}
{\renewcommand\arraystretch{1.0}
  \noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
ABL       & Atmospheric Boundary Layer \\
$\alpha$  & Wind shear exponent  \\
$f$       & Frequency \\
$f_{max}$  & Maximum resolvable frequency due to mesh limits \\
$f_{Ny}$   & Nyquist frequency \\
$L$       & Turbulent integral length scale \\
$L_{Ob}$   & Obukhov length scale \\
LES       & Large Eddy Simulation \\
$u_\tau$   & Friction velocity    \\
$\rho$    & Density \\
$\rho_\circ$ & Reference density  \\
$R_{ij}$   & Two point correlation tensor \\
SBL       & Stable Boundary Layer \\
$\theta$  & Potential temperature \\
$TI$      & Turbulence intensity \\
$TKE$     & Turbulent kinetic energy \\
$\overline{U}_{horiz}$ & Time averaged horizontal velocity
\end{longtable*}}

\section{Introduction}

@@

\subsection{Objectives}
\fxnote{fix order of objectives} In the current study on stable marine
boundary layers, we aim to build on the previous work in the
literature and complete several objectives.  First, we examine the
domain and mesh requirements necessary to capture the turbulent scales
for the stable offshore boundary layers.  Secondly, two LES solvers
within the ExaWind project will be compared in this study: the
unstructured, incompressible Navier-Stokes solver Nalu-Wind and the
structured, adaptive mesh refinement solver AMR-Wind.  Both codes are
used to calculate the same SBL, and the relative differences between
the codes are reported.  Finally, a series of stable boundary layer
conditions will be computed using AMR-Wind which match the
measurements of Archer et al. \cite{archer2016predominance}.  The
behavior of the stable boundary layers, including mean flow quantities
and turbulent statistics, are examined and compared to the neutral and
unstable cases computed in \cite{cheung2020large}.
